### 2014-11-13 language.tex
Remove dangling word.

The SSSP program starts (lines 1-3) with the declaration of the predicates.
Predicates specify the facts used in the program. The first predicate,
\mytt{edge}, is a persistent predicate that describes the
relationship between the nodes of the graph, where the third argument
represents the weight of the edge (the \mytt{route} modifier
informs the compiler that the \mytt{edge} predicate
determines the structure of the graph).  The predicates
\mytt{shortest} and \mytt{relax} are specified as linear facts
and thus are deleted when deriving new facts.  The algorithm computes
the shortest distance from node \mytt{@1} to all other nodes in the
graph. Every node has a \mytt{shortest} fact that is improved with
new \mytt{relax} facts.  Lines 5-9 declare the axioms of the
program: \mytt{edge} facts describe the graph; \mytt{shortest(A,
+00, [])} is the initial shortest distance (infinity) for all
nodes; and \mytt{relax(@1, 0, [@1])} starts the algorithm by
setting the initial distance from \mytt{@1} to \mytt{@1} to be 0.

>>>>

The SSSP program starts (lines 1-3) with the declaration of the predicates.
Predicates specify the facts used in the program. The first predicate,
\mytt{edge}, is a persistent predicate that describes the
relationship between the nodes of the graph, where the third argument
represents the weight of the edge (the \mytt{route} modifier
informs the compiler that the \mytt{edge} predicate
determines the structure of the graph).  The predicates
\mytt{shortest} and \mytt{relax} are specified as linear facts
and thus are deleted when deriving new facts.  The algorithm computes
the shortest distance from node \mytt{@1} to all other nodes in the
graph. Every node has a \mytt{shortest} fact that is improved with
new \mytt{relax} facts.  Lines 5-9 declare the axioms of the
program: \mytt{edge} facts describe the graph; \mytt{shortest(A,
+00, [])} is the initial shortest distance (infinity) for all
nodes; and \mytt{relax(@1, 0, [@1])} starts the algorithm by
setting the distance from \mytt{@1} to \mytt{@1} to be 0.
